% REQUIRED SECTION: BIOGRAPHICAL SKETCHES -- ALL IN A SINGLE TEX FILE
% This is a 1-page summary
% Use % to insert comment lines
\documentclass[11pt]{NSF}
\input{defs.tex}
\pagestyle{empty}
\begin{document}

%common commands
%\noindent
%\vspace*{0.15in}

%\section{Section A: Proposal Summary}
%start inserting text here
\begin{center}
\large\bfseries BIOGRAPHICAL SKETCH: WARREN ANDERSON
\end{center}
\hrule
\vskip 6pt
%%
%% Professional Preparation
%%
\begin{tabbing}
\parbox{\idone}{\hspace{\idone}}\=\parbox{\idtwo}{\hspace{\idtwo}} \= \kill
\textbf{Professional Preparation:}\\
\> { Ph.D.}\> Theoretical Physics. (University of Alberta, Canada. 1998) \\
\> { M.Math.}\> Applied Mathematics. (University Waterloo, Canada, 1992) \\ 
\> { M.Sc.}\> Radiological Physics. (University of Alberta. Canada, 1989) \\ 
\> { B.Sc.}\> Physcs. (University of Alberta, Canada, 1986) 
\end{tabbing}

%%
%% Appointments
%%
\begin{tabbing}{\leftmargin=3.2em\itemsep=5pt\topsep=10pt\parsep=0pt}
\parbox{\idone}{\hspace{\idone}}\=\parbox{\idtwo}{\hspace{\idtwo}} \= \kill
\textbf{Appointments:}\\
\> 2004- \>{{ Visiting Assistant Professor of Physics}, UWM}\\
\> 2003- \>{{ Visiting Assistant Professor of Physics}, UTB}\\
\> {2000-2003} \>{{ Assistant Professor of Physics}, UTB}\\
\> {1998-2000} \>{{ NSERC Postdoctoral Fellow}, University of Wisconsin -
Milwaukee} \\
\end{tabbing}

%%
%% Publications
%%
\noindent 
{\bf Five most closely related publications:}
\begin{enumerate}
%%
%%
\mypub{B.~Abbott {\it et al.}  [LIGO Scientific Collaboration]}
{Upper limits on a stochastic background of gravitational waves}
{Phys. Rev. Lett. \textbf{95} 221101 (2005), astro-ph/0507254}
%%
%%
\mypub{B.~Abbott {\it et al.}  [LIGO Scientific Collaboration]}
{Search for gravitational waves from galactic and extra-galactic
binary neutron stars}{Phys. Rev. D \textbf{72} 082001 (2005), gr-qc/0505041}
%%
%%
\mypub{B.~Abbott {\it et al.}  [LIGO Scientific Collaboration]}{
Search for gravitational waves from primordial black hole binary
coalescences in the galactic halo}{Phys.~Rev.~D. \textbf{73} 062001 (2006),
gr-qc/0505042}
%%
%%
\mypub{Charlie Torres and Warren G. Anderson}{Progress on a detection
algorithm for longer lived gravitational wave bursts}{Class.\ Quant.\ Grav.\
{\bf 22}, S1169 (2005)}
%%
%%
\mypub{B.~Abbott {\it et al.}  [LIGO Scientific Collaboration]}{
Setting upper limits on the strength of periodic gravitational waves  using
the first science data from the GEO 600 and LIGO detectors}{
Phys.\ Rev.\ D {\bf 69}, 082004 (2004), gr-qc/0308050}
\end{enumerate}
\noindent
{\bf Five other publications:}
\begin{enumerate}
%%
%%
\mypub{B.~Abbott {\it et al.}  [LIGO Scientific Collaboration]}{Limits
on gravitational wave emission from selected pulsars using LIGO data}{
Phys.\ Rev.\ Lett.\  {\bf 94}, 181103 (2005), gr-qc/0410007}
%%
%%
\mypub{B.~Abbott {\it et al.}  [LIGO Scientific
Collaboration]}{Analysis of LIGO data for gravitational waves from
binary neutron  stars}{ Phys.\ Rev.\ D {\bf 69}, 122001 (2004),
gr-qc/0308069}
%%
%%
\mypub{B.~Abbott {\it et al.}  [LIGO Scientific Collaboration]}{Upper
limits on gravitational wave bursts in LIGO's second science run}{
Phys.\ Rev.\ D {\bf 72}, 062001 (2005), gr-qc/0505029}
%%
%%
\mypub{Warren G Anderson, Patrick R Brady, Jolien Creighton and Eanna E 
Flanagan}{An excess power statistic for detection of burst sources of
gravitational radiation}{Phys.~Rev.~D \textbf{63}, 042003 (2001), 
gr-qc/0008066}
%%
%%
\mypub{Warren G. Anderson and R. Balasubramanian}{Time-frequency detection 
of gravitational waves}{Phys.~Rev.~D {\bf 55},
102001 (1999), gr-qc/9905023}
\end{enumerate}

\noindent
{\bf Synergistic Activities:}

\begin{itemize}

\item Associate Director of Center for Gravitational Wave Astronomy,
   2002-2003.
\item Member of LIGO Scientific Collaboration since 1999, including various
   committees.
\item Internal reviewer for LIGO Scientific Collaboration Stochastic Sources
   Group.
\item  Research advisor for graduate student Cristina Torres at The
   University of Texas at Brownsville.  Ph.D. awarded in 2007.
\item Have advised many undergraduate students in summer and year long
   research projects.  
\item On organizing committees for various scientific meetings, including
   2004 Gravitational Wave Data Analysis Workshop in France.
\item Reviewer for NASA and University of Chicago Press.
\item Referee for Physical Review Letters, Physical Review D, Classical and
   Quantum Gravity,  International Journal of Modern Physics, Astronomy and
   Astrophysics, Canadian Journal of Physics.
\end{itemize}

\noindent
{\bf Collaborators during the past 48 months:}

\noindent
(Not including people on above publications.)  Eanna Flanagan, Adrian
Ottewill.
\mbox{}\newline

\noindent
{\bf Anderson's Ph.D. and post-doctoral advisors:}

\noindent
Graduate Advisor: Werner Israel. Postdoctoral Advisor: Bruce Allen
\noindent

\end{document}
